Proposed Solution

### 2016-11-12 Ennan-Proposal/motivation.tex
stuff

The systems research community has recognized this as an important
problem. In fact, at this year's OSDI conference (Operating Systems
Design and Implementation, a top-tier system conference) a paper on
detecting configuration errors~\cite{xu16early} received the best paper 
award. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code.

@@

The goal of this proposal is to develop a fully {\bf {automated 
verification  framework for general software configurations}}. We plan to
overcome the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write an entire specifications for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications. Instead, we will learn specification from 
a large sample of 
configuration files. A learning process will take as input this 
sample. The process will be language-agnostic and should work for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or 
HTTPD configuration files). From that sample, we will learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties keywords in configuration files need to satisfy. One can see this learning process as 
a way of deriving  a specification for configuration files. With these  rules we can efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to a specification.

>>>>

The systems research community has recognized this as an important
problem. In fact, at this year's OSDI conference (Operating Systems
Design and Implementation, a top-tier system conference) a paper on
detecting configuration errors by emulating the late execution
 ~\cite{xu16early} received the best paper 
award. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code. Our proposal offers 
automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen.

@@

The goal of this proposal is to develop a fully {\bf {automated 
verification  framework for general software configurations}}. We plan to
overcome the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write an entire specifications for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications. Instead, we will learn specification from 
a large sample of 
configuration files. A learning process will take as input this 
sample. The process will be language-agnostic and should work for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or 
HTTPD configuration files). From that sample, we will learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties keywords in configuration files need to satisfy. One can see this learning process as 
a way of deriving  a specification for configuration files. 
It is also hard to talk here about a complete specification, but 
still having some specification is better than none, and we plan to 
increase the preciseness of a specification as we gain a better 
understanding of the formalism needed for its description.
Having a specification, we can efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to the derived specification.
